Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-10 paper/paper.tex
pass on intro

%\title{Leveraging Diversity to Find Bugs in JavaScript Engines}
\title{Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing}
%\titlerunning{Leveraging Diversity to Find Bugs in JavaScript Engines}        % if too long for running head

@@

The study measures the ability of these techniques in finding bugs and
the impact of false positives on their practicality. \Mar{seria bom
  adicionar uma frase com rationale para escolha destas tecnicas.}

@@

Table~\ref{tab:test-suites} shows the breakdown of tests per
engine. Column ``full'' shows the number of test cases associated with
each engine. Column ``pass-in-par.''  shows the number of test cases
that pass in their parent engine. We discarded tests that fail in
their parent engine as we could not reliably indicate the reason for
the failure, so we assumed the test could be broken. We removed \testsThatFail{}
test cases that fail for that reason--\testsThatFailJSC{} tests from \jsc and
\testsThatFailSM{} tests from \smonkey. Column ``type-in-all''
shows the number of test cases whose executions do not throw
dynamic type errors in any of the engines because of an undefined variable or property.
These cases were captured by looking for the presence of \CodeIn{ReferenceError} and
\CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
(respectively, \CodeIn{TypeError}) is raised when test execution
attempts to access an undefined variable (respectively, property of an
object). We discarded those tests to avoid noise in the experiments as
they clearly indicate some missing feature as opposed to bugs. For
example, some tests use non-portable names (\eg{}, \jsc's
\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
or use functions that, albeit part of the spec, not all engines
currently support. \Fix{Similarly, the \chakra project does not use the default
well-known assertions available in JS, which the other JS engines use.
Instead, it uses its own testing framework, WScript. In this case, we could
not easily reproduce the \chakra unit tests in the other engines since it would
raise a ReferenceError. Also, updating the other engines to use WScript would
require a non-trivial manual process. This is why \chakra is not showed
in Table~\ref{tab:test-suites}.}

@@

\Fix{Figure~\ref{fig:lo-truepositive} shows a test was originally
available in the \jsc codebase.  The \radamsa fuzzing technique
mutated the test. In particular, it introduced the negative
long \texttt{-1770523502845470856} as a parameter of the
\texttt{view.getInt8()} method. Before the mutation, the
\texttt{view.getInt8()} method received a zero integer.}
At the botom of this figure, there is a sequence of
three elements that we use to characterize a warning--1) the
identifier of an engine, 2) the exception it raises, and 3) the
message it produces on a ``\lo'' warning.  This sequence of triples
defines a warning signature that we use for clustering. It is worth
mentioning that we filter references to code in messages as to
increase ability to aggregate warnings. Any warnings, including this
one, that has this same signature will be included in the same
``bucket''. Considering the example from
Figure~\ref{fig:lo-truepositive}, the signature for that cluster will
be [(JavaScriptCore, ``RangeError'', ``byteOffset cannot be
  negative''), (SpiderMonkey, ``RangeError'', ``invalid or
  out-of-range index''), (V8, ``RangeError'', ``Offset is outside the
  bounds of the DataView'')].

@@

The ECMA Test262~\cite{ecma262-conformance-suite} test suite serves to
check conformance of engines to the \js\ standard. It is
acceptable to release engines fulfilling the specification only
partially~\cite{kangax}. We expect that the pass rate on this suite
provide some indication of the engine's maturity. In the limit, it is
not desirable to flood bug reports on engines at early stages of
development.

For this experiment, we ran the suite once a day for seven consecutive
days and averaged the passing ratios. Table~\ref{tab:test262} shows
the average number of passing tests over this period. The variance of
results was negligible; for that reason, we omitted standard
deviations. We noticed that all four engines but \chakra{} used some
variant of the Test262 suite as part of their regression process, but
we used the same version in this
experiment~\cite{ecma262-conformance-suite}.

\begin{table}
  %\vspace{-4ex}
  \centering
  \caption{\label{tab:test262}Percentage of passing tests on
    the Test262 conformance suite.}
  %\small
  \begin{tabular}{rr}
    \toprule
    engine & \% passing \\
    \midrule
    \jsc & \percentSuiteTestJSC{}\\
    \veight{} & \percentSuiteTestVeight{} \\
    \chakra{} & \percentSuiteTestChakra{} \\
    \smonkey{} & \percentSuiteTestSM{} \\
    \hermes & xxx \\
    \bottomrule
  \end{tabular}
  %\normalsize
\end{table}

Results show that there are still many unsupported scenarios as can be observed from the
percentages in the table. The number of passing tests is high and
similar for \jsc, \veight{}, and \smonkey\ whereas \chakra\ performs
worse compared to the other engines. Note also that \chakra\ is both
the engine that has the lowest passing ratio in this test suite and
the one we were able to find more bugs (as per
Figure~\ref{fig:summary}). Although it is plausible to find
correlation between the passing ratios and reliability as measured by
the number of bugs found, we do not imply causality. It is important
to note that failures in this conformance test suite indicates missing
features as opposed to bugs.

\begin{center}
  \fbox{
    \begin{minipage}{8cm}
      \textit{Summary:}~All engines seem to adhere well to the
      \js\ standard. Except for \chakra, the passing ratio of all
      engines is above 90\%.
      \end{minipage}
    }
\end{center}

@@

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:cross-testing}Number of failures with
    Test Transplantation.}
  \renewcommand*{\arraystretch}{0.9}
  \begin{tabular}{crrrr}
    \toprule
    test suite\textbackslash{}engine & \jsc & \veight{} & \smonkey{} & \chakra{}\\
    \midrule
    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
    \Comment{
      Lembrar dos testes que os testes da propria engine falham:
      V8 0
      JSC 2
      Spidermonkey 58
    }
    \jsc & - & 10 & 10 & 59   \\
    \veight{} & 41 & - & 3 & 5  \\
%    \chakra{} & - & - & - & -  \\
    \smonkey{} & 218 & 107 & - & 281 \\
    Duktape & 0 & 4 & 4 & 1   \\
    \jerry{} & 23 & 25 & 22 & 23   \\
    JSI & 0 & 0 & 0 & 0   \\
   Tiny-js & 0 & 0 & 0 & 0  \\
    \midrule
   \textbf{total} & 282 & 146 & 39 & 369 \\
    \bottomrule
  \end{tabular}
  \vspace{-3ex}
\end{table}

@@

Table~\ref{tab:cross-testing} shows the number of failures observed
for each pair of test suite and engine. The first column shows the
test suites and the first row shows the engines that run those
tests. We use a dash (``-'') to indicate that we did not consider the
combinations that associate a test suite with its parent engine;
failures in those cases would either indicate regressions or flaky
tests as opposed to unknown bugs for that engine. As explained in
Section~\ref{sec:seeds}, we used in this experiment the
\totalTestFilesForTestTransplantation{} tests included in the
rectangle area under column ``type-in-all'' from
Table~\ref{tab:test-suites}. Running those tests we observed a total
of \failuresTestTrans{} failures manifested across
\failuresTestTransDistictFiles{} distinct files
(\failuresTestTransPercent{} of total).  Table~\ref{tab:cross-testing}
shows that \smonkey\ was the engine that failed the least whereas
\chakra\ was the engine that failed the most. The \smonkey\ test suite
also revealed more failures than any other, as expected, given
that it is the suite with more tests (see
Table~\ref{tab:test-suites}).

@@

\begin{table}[t]
  \small
  \setlength{\tabcolsep}{4.5pt}
  \centering
  \caption{\label{tab:summary-hi}Number of \hi\ warning
    reports per engine.}
  \begin{tabular}{crrrrr}
    \toprule
    fuzzer\textbackslash{}engine & \jsc\ & \veight\ & \chakra & \smonkey & +1\\
    \midrule
    \radamsa{} & 151 & 50 & 331 & 94 & 628 \\ % 137 & 47 & 323 & 21 & 483
    \quickfuzz{} & 83 & 63 & 351 & 21 & 403 \\ % 81 & 62 & 349 & 13 & 369
    \midrule
    \textbf{total} & 234 & 113 & 682 & 115 & 1031 \\ % 218 & 109 & 672 & 34 & 852
    \bottomrule
  \end{tabular}
\end{table}

@@

Table~\ref{tab:bugs} shows the list of bugs we reported. The table
shows the fuzzing tool used
(``Fuzzer''), the \js\ engine affected (``Engine''), the status of the
bug report (``Status'')\Comment{ as of Aug. 24, 2018, the Url of the bug report
(``Url'')}, the severity of the bug report (``Sev.''), the priority
that we assigned to the warning that revealed the bug (``Priority''),
and the test suite from the original test input (``Suite''). So far,
\noDiffConfirmed{} of the bugs we reported were confirmed, \noDiffFixed{} of which
were fixed. Note that one bug report that we submitted was rejected on
the basis that the offending JS file manifested an incompatibility
across engine implementations that was considered to be acceptable. As
of now, we did not find any new bugs on \smonkey{}; the bugs we found
were duplicates and were not reported. For \veight{},
we reported \noDiffVeight{} bugs,
all of them confirmed, with \noDiffVeightFixed{} fixed.

@@

This is a testcase original from the \jsc suite that the
\radamsa\ fuzzer modified. The original test used the integer literal
3 as argument to \CodeIn{repeat()}, but this test uses a long integer
instead. As result, the engine crashes. The team answered that this
was an incompatibility by design as the function was not expected to
receive such a long value.

@@

In the near future, we plan to explore techniques to prioritize the
warnings reported by these techniques and to continue involving
students in the task of diagnosing these warnings. Using learning
techniques for prioritization, similar to what Chen and
colleagues~\cite{Chen:2017:LPT:3097368.3097451} did to prioritize the
warnings reported by CSmith~\cite{Yang:2011:FUB:1993498.1993532},
seems a promising starting point for this improvement.

@@

%%  LocalWords:  IoT DT JS JIT fuzzer jsfunfuzz jit funfuzz bytecodes
%%  LocalWords:  JavaScriptCore JScript Ecma toPrecision Kangax JSVU
%%  LocalWords:  cccrr WebKit ReferenceError TypeError lineNumber sep
%%  LocalWords:  drainMicrotasks ccrrrr Duktape js runtime formedness
%%  LocalWords:  NN NLP vec embeddings perceptron arrowed toolchain
%%  LocalWords:  fuzzers eshost cli pre ArrayBuffer RangeError getInt
%%  LocalWords:  ToIndex Clusterization byteOffset SpiderMonkey AFL
%%  LocalWords:  DataView setInt Radamsa QuickFuzz Grammarinator de
%%  LocalWords:  LangFuzz Megadeth libFuzzer sanitizers Breno
% LocalWords:  d'Amorim Universidade Pernambuco

>>>>

%\title{Leveraging Diversity to Find Bugs in JavaScript Engines}
\title{Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing}
\titlerunning{Exposing Bugs in JavaScript Engines}        % if too long for running head

@@

These techniques demand different effort from developers. Cross-engine
differential testing is semi-automated as developers need to decide if
alarms are manifestations of real bugs. Test transplantation is fully
automated, but it can only reveal bugs that the original tests could
reveal. This study measures the ability of these techniques in finding
bugs and the human cost associated with each technique.

@@

Table~\ref{tab:test-suites} shows the breakdown of tests per
engine. Column ``full'' shows the number of test cases associated with
each engine. Column ``pass-in-par.''  shows the number of test cases
that pass in their parent engine. We discarded tests that fail in
their parent engine as we could not reliably indicate the reason for
the failure, so we assumed the test could be broken. We removed \testsThatFail{}
test cases that fail for that reason--\testsThatFailJSC{} tests from \jsc and
\testsThatFailSM{} tests from \smonkey. Column ``type-in-all''
shows the number of test cases whose executions do not throw
dynamic type errors in any of the engines because of an undefined variable or property.
These cases were captured by looking for the presence of \CodeIn{ReferenceError} and
\CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
(respectively, \CodeIn{TypeError}) is raised when test execution
attempts to access an undefined variable (respectively, property of an
object). We discarded those tests to avoid noise in the experiments as
they clearly indicate some missing feature as opposed to bugs. For
example, some tests use non-portable names (\eg{}, \jsc's
\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
or use functions that, albeit part of the spec, not all engines
currently support. \Fix{Similarly, the \chakra project does not use the default
well-known assertions available in JS, which the other JS engines use.
Instead, it uses its own testing framework, WScript. In this case, we could
not easily reproduce the \chakra unit tests in the other engines since it would
raise a \texttt{ReferenceError}. Also, updating the other engines to use WScript would
require a non-trivial manual process. This is why \chakra is not showed
in Table~\ref{tab:test-suites}.}

@@

\Fix{Figure~\ref{fig:lo-truepositive} shows a test was originally
available in the \jsc code base.  The \radamsa fuzzing technique
mutated the test. In particular, it introduced the negative
long \texttt{-1770523502845470856} as a parameter of the
\texttt{view.getInt8()} method. Before the mutation, the
\texttt{view.getInt8()} method received a zero integer.}
At the bottom of this figure, there is a sequence of
three elements that we use to characterize a warning--1) the
identifier of an engine, 2) the exception it raises, and 3) the
message it produces on a ``\lo'' warning.  This sequence of triples
defines a warning signature that we use for clustering. It is worth
mentioning that we filter references to code in messages as to
increase ability to aggregate warnings. Any warnings, including this
one, that has this same signature will be included in the same
``bucket''. Considering the example from
Figure~\ref{fig:lo-truepositive}, the signature for that cluster will
be [(JavaScriptCore, ``RangeError'', ``byteOffset cannot be
  negative''), (SpiderMonkey, ``RangeError'', ``invalid or
  out-of-range index''), (V8, ``RangeError'', ``Offset is outside the
  bounds of the DataView'')].

@@

The ECMA Test262~\cite{ecma262-conformance-suite} test suite serves to
check conformance of engines to the \js\ standard. It is
acceptable to release engines fulfilling the specification only
partially~\cite{kangax}. We expect that the pass rate on this suite
provide some indication of the engine's maturity. In the limit, it is
not desirable to flood bug reports on engines at early stages of
development.
\Fix{For this experiment, we ran the suite once a day for seven consecutive
days and averaged the passing ratios.
We performed seven consecutive executions because,
since the studied JS engines release new versions on a daily basis,
we wanted to make sure if the failing tests raised by the Test262 suite
were rapidly fixed by the maintenance team. If these errors were quickly
fixed, that would suggest that this given engine would be aligned with
the ECMAScript specification.}
Table~\ref{tab:test262} shows
the average number of passing tests over this period. The variance of
results was negligible; for that reason, we omitted standard
deviations. We noticed that all four engines but \chakra{} used some
variant of the Test262 suite as part of their regression process, but
we used the same version in this
experiment~\cite{ecma262-conformance-suite}.

\begin{table}
  %\vspace{-4ex}
  \centering
  \caption{\label{tab:test262}Percentage of passing tests on
    the Test262 conformance suite.}
  %\small
  \begin{tabular}{rr}
    \toprule
    engine & \% passing \\
    \midrule
    \jsc & \percentSuiteTestJSC{}\\
    \veight{} & \percentSuiteTestVeight{} \\
    \chakra{} & \percentSuiteTestChakra{} \\
    \smonkey{} & \percentSuiteTestSM{} \\
    \hermes & \percentSuiteTestHermes{} \\
    \bottomrule
  \end{tabular}
  %\normalsize
\end{table}

%Nao envolver o hermes nos experimentos antigos pq o hermes vai
%lancar erros pq a funcionalidade não foi implementada

Results show that there are still many unsupported scenarios as can be observed from the
percentages in the table. The number of passing tests is high and
similar for \jsc, \veight{}, and \smonkey\ whereas \hermes performs
worse when compared to the other engines.
\Fix{This happens because \hermes
still has many unsupported features, such as Proxy, Promisse, and Async.}
Moreover, one can also note that \chakra\ also a low passing ratio
in this test suite and the one we were able to find more bugs (as per
Figure~\ref{fig:summary}). Although it is plausible to find
correlation between the passing ratios and reliability as measured by
the number of bugs found, we do not imply causality. As aforementioned,
it is important
to note that failures in this conformance test suite indicates missing
features as opposed to bugs.

\begin{center}
  \fbox{
    \begin{minipage}{8cm}
      \textit{Summary:}~Most of the engines seem to adhere well to the
      \js\ standard. Except for \hermes and \chakra, the passing ratio of all
      engines is above 90\%.
      \end{minipage}
    }
\end{center}

@@

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:cross-testing}Number of failures with
    Test Transplantation.}
  \renewcommand*{\arraystretch}{0.9}
  \begin{tabular}{crrrrr}
    \toprule
    test suite\textbackslash{}engine & \jsc & \veight{} & \smonkey{} & \chakra{} & \hermes{} \\
    \midrule
    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
    \Comment{
      Lembrar dos testes que os testes da propria engine falham:
      V8 0
      JSC 2
      Spidermonkey 58
    }
    \jsc & - & 10 & 10 & 59 & 340  \\
    \veight{} & 41 & - & 3 & 5 & 315 \\
%    \chakra{} & - & - & - & -  \\
    \smonkey{} & 218 & 107 & - & 281 & - \\
    Hermes & 8 & 14 & 8 & 26 & -  \\
    Duktape & 0 & 4 & 4 & 1 & 140  \\
    \jerry{} & 23 & 25 & 22 & 23 & 311  \\
    JSI & 0 & 0 & 0 & 0 & 40\\
   Tiny-js & 0 & 0 & 0 & 0 & 10  \\
    \midrule
   \textbf{total} & 290 & 160 & 47 & 395 & 1156 \\
    \bottomrule
  \end{tabular}
  \vspace{-3ex}
\end{table}

@@

Table~\ref{tab:cross-testing} shows the number of failures observed
for each pair of test suite and engine. The first column shows the
test suites and the first row shows the engines that run those
tests. We use a dash (``-'') to indicate that we did not consider the
combinations that associate a test suite with its parent engine.
\Fix{
In particular, we were not able to reuse the \smonkey tests on the
\hermes engine. This happened because \smonkey has its own assertion
framework, but \hermes did not interpret these assertions, resulting
in failures in all test executions from this engine. These failures
did not happen when the \smonkey tests were transplanted to the other engines,
though.
}
failures in those cases would either indicate regressions or flaky
tests as opposed to unknown bugs for that engine. As explained in
Section~\ref{sec:seeds}, we used in this experiment the
\totalTestFilesForTestTransplantation{} tests included in the
rectangle area under column ``type-in-all'' from
Table~\ref{tab:test-suites}. Running those tests we observed a total
of \failuresTestTrans{} failures manifested across
\failuresTestTransDistictFiles{} distinct files
(\failuresTestTransPercent{} of total).  Table~\ref{tab:cross-testing}
shows that \smonkey\ was the engine that failed the least whereas
\chakra\ was the engine that failed the most. The \smonkey\ test suite
also revealed more failures than any other, as expected, given
that it is the suite with more tests (see
Table~\ref{tab:test-suites}).

@@

\begin{table}[t]
  \small
  \setlength{\tabcolsep}{4.5pt}
  \centering
  \caption{\label{tab:summary-hi}Number of \hi\ warning
    reports per engine.}
  \begin{tabular}{crrrrr}
    \toprule
    fuzzer\textbackslash{}engine & \jsc\ & \veight\ & \chakra & \smonkey & +1\\
    \midrule
    \radamsa{} & 151 & 50 & 331 & 94 & 528 \\ % 137 & 47 & 323 & 21 & 483
    \quickfuzz{} & 83 & 63 & 351 & 21 & 403 \\ % 81 & 62 & 349 & 13 & 369
    \midrule
    \textbf{total} & 234 & 113 & 682 & 115 & 931 \\ % 218 & 109 & 672 & 34 & 852
    \bottomrule
  \end{tabular}
\end{table}

@@

Table~\ref{tab:bugs} shows the list of bugs we reported. The table
shows the fuzzing tool used
(``Fuzzer''), the \js\ engine affected (``Engine''), the status of the
bug report (``Status'')\Comment{ as of Aug. 24, 2018, the URL of the bug report
(``URL'')}, the severity of the bug report (``Sev.''), the priority
that we assigned to the warning that revealed the bug (``Priority''),
and the test suite from the original test input (``Suite''). So far,
\noDiffConfirmed{} of the bugs we reported were confirmed, \noDiffFixed{} of which
were fixed. Note that one bug report that we submitted was rejected on
the basis that the offending JS file manifested an incompatibility
across engine implementations that was considered to be acceptable. As
of now, we did not find any new bugs on \smonkey{}; the bugs we found
were duplicates and were not reported. For \veight{},
we reported \noDiffVeight{} bugs,
all of them confirmed, with \noDiffVeightFixed{} fixed.

@@

This is a test case original from the \jsc suite that the
\radamsa\ fuzzer modified. The original test used the integer literal
3 as argument to \CodeIn{repeat()}, but this test uses a long integer
instead. As result, the engine crashes. The team answered that this
was an incompatibility by design as the function was not expected to
receive such a long value.

@@

In the near future, we plan to explore techniques to prioritize the
warnings reported by these techniques and to continue involving
students in the task of diagnosing these warnings. Using learning
techniques for prioritization~\cite{icst2020violations}, 
similar to what Chen and colleagues~\cite{Chen:2017:LPT:3097368.3097451} 
did to prioritize the warnings reported by CSmith~\cite{Yang:2011:FUB:1993498.1993532},
seems a promising starting point for this improvement.

@@

%%  LocalWords:  IoT DT JS JIT fuzzer jsfunfuzz jit funfuzz bytecodes
%%  LocalWords:  JavaScriptCore JScript Ecma toPrecision Kangax JSVU
%%  LocalWords:  cccrr WebKit ReferenceError TypeError lineNumber sep
%%  LocalWords:  drainMicrotasks ccrrrr Duktape js runtime formedness
%%  LocalWords:  NN NLP vec embeddings perceptron arrowed toolchain
%%  LocalWords:  fuzzers eshost cli pre ArrayBuffer RangeError getInt
%%  LocalWords:  ToIndex Clusterization byteOffset SpiderMonkey AFL
%%  LocalWords:  DataView setInt Radamsa QuickFuzz Grammarinator de
%%  LocalWords:  LangFuzz Megadeth libFuzzer sanitizers Breno cccrrr
% LocalWords:  d'Amorim Universidade Pernambuco JerryScript JSI RQ FP
% LocalWords:  WScript conformant TP ccr OME FPs TPs crrrrr ccrr NaN
% LocalWords:  ascii unary ToNumber valueOf eval SyntaxError iterable
% LocalWords:  escapeinside basicstyle boxpos numberstyle assertEq
% LocalWords:  morekeywords typeof instanceof foofoofoo TinyJS SSL
% LocalWords:  TLS Lidbury OpenCL SIMD GPUs Purdom parsers Lammel APQ
% LocalWords:  Shulte Geno XPath combinatorial CSmith LLVM Patra CNPq
% LocalWords:  disassemblers Pradel namespaces Eshkevari FACEPE
% LocalWords:  PRONEX
